\subsection*{What is NCLab?}
NCLab is a popular Online STEM Laboratory that serves thousands of students, instructors and 
researchers all over the world. It helps its users complete projects in many STEM fields ranging from
symbolical and numerical mathematics, computer simulations in physics and chemistry, 3D computer 
aided design (CAD), computer programming, and web design to engineering-level computer simulations 
in various areas including solid mechanics, fluid dynamics, electromagnetics, neutronics and others. 
NCLab can be used {\bf free of charge for personal non-commercial purposes} such as private 
hobby or self-education, as well as for individual non-funded academic research.

\noindent
\subsection*{Why is NCLab Not Free for Institutions?}
NCLab differs from standard commercial products in related areas in that it provides both 
{\bf functionality} and {\bf resources}. Resources include cloud storage, memory, 
CPU time and even web hosting. Therefore, institutions need to {\bf purchase a license} 
prior to using NCLab in classroom, for research, or for commercial projects (see Terms of Use and 
Pricing). These fees are very small compared to traditional commercial products in related areas. 

\subsection*{Terms of Use and Pricing}
More details on purchasing a license and using NCLab are provided in the online documents 
{\bf Pricing} and {\bf Terms of Use} that are accessible from NCLab's home page 
{\tt http://nclab.com}.

\subsection*{FEMhub Inc.}

NCLab is a product of FEMhub Inc. The name "NCLab" is 
registered with the U.S. Patent and Trademark Office (USPTO) under Trademark No. 85420518.

\subsection*{Contact Information}
General inquiries: {\tt info@femhub.com}\\
Sales: {\tt sales@femhub.com}\\
NCLab support: {\tt support@nclab.com}\\
Agros \& Hermes support: {\tt support@femhub.com}\\
Web page: {\tt http://femhub.com}\\
{Physical address}\\
FEMhub Inc.\\
5490 Twin Creeks Dr.\\
Reno, NV 89523

\subsection*{About This Publication}
This publication can be copied and distributed without any restrictions
as long as reference to NCLab and FEMhub Inc. is preserved.
